%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\pagebreak
\cvsection{Noteworthy scientific communications}

%-------------------------------------------------------------------------------
%	SUBSECTION TITLE
%-------------------------------------------------------------------------------
\cvsubsection{Invited seminars}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvhonors}

\cvhonor{Overview of simulation methods for modeling of radiation damage in silicon detectors}{Inter-experiment workshop on Radiation Effects in LHC Experiments,CERN}
{Geneva, Switzerland}
{Feb. 2019}

\cvhonor{CMOS pixel development for the ATLAS experiment at the HL-LHC and CLIC Vertex and tracker}{Argonne National Laboratory, HEP Division seminar}
{Chicago, IL, USA}
{Apr. 2017}

\cvhonor{Simulation of Silicon detectors using TCAD and Monte-Carlo methods}{DESY Detector seminar}
{Hamburg, Germany}
{Sept. 2016}

\cvhonor{Simulation of Silicon detectors using TCAD and Monte-Carlo methods}{CERN Detector seminar}
{Geneva, Switzerland}
{June 2016}

\cvhonor{Research and development on vertex detector technology for the Compact Linear Collider (CLIC)}
{LAL}
{Orsay, France}
{Feb. 2013}

\cvhonor{TCAD Simulation of irradiated Silicon radiation detector using commercial simulation products}
{20th RD50 Collaboration meeting}
{Bari, Italy}
{May 2012}

\cvhonor{Technology-Computer Assisted Design (TCAD) and Monte-Carlo (MC) simulation of semiconductor detectors for high energy and nuclear physics applications}
{Gottingen II. Institute of Physics}
{Gottingen, Germany}
{Feb. 2011}

\cvhonor{Mise \`a jour du d\'etecteur interne d'ATLAS pour son operation \`a haute luminosit\'e}
{Particle Physics Laboratory Seminar, University of Montreal}
{Montreal, Qc, Canada}
{Jan. 2010}

\cvhonor{Formation aux outils de simulation Silvaco TCAD Omni}
{Centre de d\'eveloppement des technologies avanc\'ees de Alger (CTDA)}
{Algiers, Algeria}
{June 2009}

\cvhonor{Mod\'elisation des signaux et du partage de charge dans les dispositifs de d\'etection \`a base de CZT par une m\'ethode hybride de simulation Monte-Carlo/elements finis}
{LAL}
{Orsay, France}
{June 2008}

\end{cvhonors}
\cvsubsection{Invited presentation in international conferences}

\begin{cvhonors}
\cvhonor{Pixel-detector R\&D for CLIC}
{PIXEL2018}
{Taipei, Taiwan}
{Dec. 2018}

\cvhonor{The Phase-2 ATLAS ITk Pixel Upgrade}
{TIPP 2017}
{Beijing, China}
{May 2017}

\cvhonor{HV and HR-CMOS sensor technology R\&D for ATLAS ITk}
{Vertex 2015}
{Santa Fe, NM, USA}
{Aug. 2015}

\cvhonor{TCAD Simulation of CCPD family of HVCMOS sensors}
{Trento Workshop on advanced Silicon detectors}
{Trento, Italy}
{Feb. 2015}

\cvhonor{TCAD Simulation of Silicon Radiation Detectors using commercial simulation products}
{Vertex 2013}
{Lake Starnberg, Germany}
{Sept. 2013}

\cvhonor{Vertex detectors for the future linear colliders}
{PIXEL2012 Conference}
{Inawashiro, Japan}
{Sept. 2012}

\end{cvhonors}

\cvsubsection{Other presentations}
\begin{cvhonors}
\cvhonor{Characterization of the 180nm HV-CMOS ATLASPix large-fill factor Monolithic prototype}
{TREDI19}
{Trento, Italy}
{Feb. 2019}

\cvhonor{Test-beam characterization, calibration and simulation for hybrid-pixel readout assemblies with ultra-thin sensors}
{PIXEL2014}
{Niagara Falls, On, Canada}
{Aug. 2014}

\cvhonor{Test beam characterization of Ultra-Thin hybrid pixel Timepix assemblies for CLIC Vertex R\&D}
{Trento Workshop on advanced Silicon detectors}
{Genova, Italy}
{Feb. 2014}

\cvhonor{Vertex detector R\&D for CLIC}
{LCWS13}
{Tokyo, Japan}
{Nov. 2013}

\cvhonor{Simulation of charge multiplication and trap-assisted tunneling in irradiated n-in-p planar pixel sensors}
{IEEE NSS 2010}
{Knoxville, TN, USA}
{Nov. 2010}

\cvhonor
{Simulation of charge multiplication and trap-assisted tunneling in irradiated n-in-n planar pixel detectors}
{5th Trento Workshop on Advanced silicon detectors}
{Manchester,UK}
{Feb. 2010}

\cvhonor{Simulation of multi guard ring structure in p-type pixel sensor for ATLAS inner tracker upgrade,}
{4th Trento Workshop on Advanced silicon detectors}
{Trento, Italy}
{Feb. 2009}

\cvhonor{Simulation of guard ring influence on the performance of ATLAS pixel detectors for inner layer replacement}
{PIXEL2008}
{Chicago, IL, USA}
{Sept. 2008}

\cvhonor{CdZnTe for $\gamma$ ray imagery: Simulation of pixel size influence on charge-sharing by hybrid Monte-Carlo and finite element method}
{NDIP08}
{Aix-Les-Bains, France}
{June 2008}


\end{cvhonors}







% %-------------------------------------------------------------------------------
% %	SUBSECTION TITLE
% %-------------------------------------------------------------------------------
% \cvsubsection{Domestic}


% %-------------------------------------------------------------------------------
% %	CONTENT
% %-------------------------------------------------------------------------------
% \begin{cvhonors}

% %---------------------------------------------------------
%   \cvhonor
%     {3rd Place} % Award
%     {WITHCON Hacking Competition Final} % Event
%     {Seoul, S.Korea} % Location
%     {2015} % Date(s)

% %---------------------------------------------------------
%   \cvhonor
%     {Silver Prize} % Award
%     {KISA HDCON Hacking Competition Final} % Event
%     {Seoul, S.Korea} % Location
%     {2013} % Date(s)

% %---------------------------------------------------------
% \end{cvhonors}
