%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------

\cvsection{Student supervision}


\begin{cvhonors}

\cvhonor{Mateus Vicente, PhD Thesis}{HV-CMOS detector development for future experiments, in redaction}{Uni.of Geneva}{2019}
\cvhonor{Francesco di Bello, PhD Thesis}{Search for scalar and axial resonances decaying into a pairs of b quarks using the ATLAS detector at the LHC and studies on CMOS pixel sensor for HL-LHC, in redaction}{Uni. of Geneva}{2019}
\cvhonor{Lingxin Meng, PhD Thesis}{Development of CMOS Sensors for High-Luminosity ATLAS Detectors}{Uni. of Geneva \& Uni. of Liverpool}{2018}
\cvhonor{Matthew Buckland, PhD Thesis}{Simulation and evaluation of HV-CMOS pixel sensors for the CLIC vertex detector}{Uni. of Liverpool \& CERN (CLICdp)}{2018}
\cvhonor{Branislav Ristic, PhD Thesis}{Nocel Pixel Sensors in HV-CMOS Technology and Testbeam Infrastructure for Upgrades of the ATLAS Inner Tracking System}{University of Geneva}{2018}
\cvhonor{Niloufar Alipour, PhD Thesis}{Test-beam measurements and simulation studies of thin pixel sensors for the CLIC vertex detector}{ETH Zurich \& CERN (CLICdp)}{2017}
\cvhonor{Javier de Bilbao, PhD Thesis}{Production, integration and commissioning of the ATLAS Insertable B-Layer and test beam studies of new pixel technologies for the HL-LHC}{Uni. of Geneva}{2016}
\cvhonor{Le Li, Msc Thesis}{TCAD and Monte-Carlo simulation of the ATLASPix prototype}{Uni. of Geneva}{2019}
\cvhonor{Nicolas Terasson, Msc Thesis}{Monte-Carlo simulation of the FEI4 Telescope}{Uni. of Geneva}{2018}
\cvhonor{Francesco di Bello, Msc Thesis}{Simulation, reconstruction and analysis of HV-CMOS pixel detector prototype data with the FEI4 Telescope}{Uni. of Geneva}{2016}
\cvhonor{Misael Caloz, Msc Thesis}{Equalisation algorithms for the CCPDv4 HV-CMOS pixel sensor prototype}{Uni. of Geneva}{2016}
\cvhonor{Niloufar Alipour, Msc Thesis}{Simulation of novel planar pixel sensors with active-edge for Timepix}{ETH Zurich \& CERN (CLICdp)}{2015}

\end{cvhonors}
